\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-17 k-planar.tex
Change suggested by Vida

	In the general case, our $H$-partition $\mathcal{P}$ will include $P_1$, $P_2$ , $P_3$ and a (possibly empty) part $S$ that is defined by three vertices $v_1v_2v_3$ that belong to a common inner face $\tau$ of $N'$.  There is one case to consider for each possible value of $k$ (see \cref{boring_figure}):
	\begin{compactenum}
		\item If $k=1$ then we let $\tau:=v_1,\ldots,v_p$ be an inner face of $N'$ that contains at least one edge $v_1v_2$ of $F$ on its boundary.

>>>>

	In the general case, our $H$-partition $\mathcal{P}$ will include $P_1$, $P_2$ , $P_3$ and a (possibly empty) part $S$ that will be determined by three vertices $v_1v_2v_3$ that belong to a common inner face $\tau$ of $N'$.  We first explain how $v_1$, $v_2$ and $v_3$ are chosen and explain how these are used to define $S$.  There is one case to consider for each possible value of $k$ (see \cref{boring_figure}):
	\begin{compactenum}
		\item If $k=1$ then we let $\tau:=v_1,\ldots,v_p$ be an inner face of $N'$ that contains at least one edge $v_1v_2$ of $F$ on its boundary.
